---
title: "Estimation of parameter importance with fANOVA"
author: "Marcus Ritt"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(kableExtra)
library(ggplot2)
source("../functions.R")
```

```{r, include=FALSE}
dataset="test1/irace-acotsp1000-4500-1" # this one has no replications
dataset="test2/irace-acotsp1000-4500-1"
dataset="test3/acotsp1000-4500-01"
use.ranks=TRUE
```

(For dataset: `r dataset`.)

## 1. Analysis of a single run

### 1.1. Dependent variable: raw performance

```{r}
importanceTable(dataset,"perf")
```

### 1.2. Dependent variable: normalized performance

```{r}
importanceTable(dataset,"norm")
```

### 1.3. Dependent variable: performance quantile

```{r}
importanceTable(dataset,"quan")
```

### 1.4. Dependent variable: normalized ranking

```{r}
importanceTable(dataset,"rank")
```

### 1.5. Dependent variable: normalized ranking with imputation

```{r}
importanceTable(dataset,"irank")
```

### 1.6. Dependent variable: ranking quartile with imputation

```{r}
importanceTable(dataset,"qrank")
```

## 2. Comparison of measures among a single run

```{r}
bumpChartMeasures(dataset,do.rank=use.ranks)
```

## 3. Comparison of five replications


### 3.1. Dependent variable: raw performance

```{r}
bumpChartReplications(dataset,"perf",do.rank=use.ranks)
```

### 3.2. Dependent variable: normalized performance

```{r}
bumpChartReplications(dataset,"norm",do.rank=use.ranks)
```

### 3.3. Dependent variable: performance quantile

```{r}
bumpChartReplications(dataset,"quan",do.rank=use.ranks)
```

### 3.4. Dependent variable: normalized ranking

```{r}
bumpChartReplications(dataset,"rank",do.rank=use.ranks)
```

### 3.5. Dependent variable: normalized ranking with imputation

```{r}
bumpChartReplications(dataset,"irank",do.rank=use.ranks)
```

### 3.6. Dependent variable: ranking quartile with imputation

```{r}
bumpChartReplications(dataset,"qrank",do.rank=use.ranks)
```
